\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-09-29 coqimpl.tex
a question

Importantly, the recursor field (e.g. "subst") is not actually
inheritable, because it is not compiled like any other fields.
Recall how other fields are compiled into reusable pieces of
(parametrized) modules; a recursor field is not compiled like that.
For all the children family, we have to reconstruct and override the
"FRecursor" field with a ``new'' recursor using (maybe the same) handler
family.  This is affordable since each aggregated recursor handler
doesn't need to be rechecked---look at "STLC_bool.neg_handler", there
are only  new handlers for "tm_true" and the handlers (mundane fields)
from the parent "B.subst_internal.tm_var" have already been type-checked
and inherited (since they only rely on ``the abstracted interface''
module "STLC_409"). 
Thanks to family inheritance, their corresponding compiled module from the parents---for example, 
the module "tm_var_411"---doesn't require another type-check and is
re-used during the type-checking and compilation of "STLC_bool.subst".
For example, for the new "subst", when compiling family "STLC_bool" into
a module, at the appropriate place our plugin will insert
\begin{minted}{Coq}
Definition subst := tm_rec (λ _ ⇒ id → tm → tm) subst_internal.tm_var ...
\end{minted}
where "tm_rec" and "tm" are the corresponding recursor and the (vanilla
but extended and modified) inductive type in that compiled module. Note
that, even though "tm_rec" and "tm" has the same name as before, they
are in the newly-compiled module so they refer to totally different
things.

>>>>

Importantly, the recursor field (e.g. "subst") is not actually
inheritable, because it is not compiled like any other fields.
Recall how other fields are compiled into reusable pieces of
(parametrized) modules; a recursor field is not compiled like that.
For all the children family, we have to reconstruct and override the
"FRecursor" field with a ``new'' recursor using (maybe the same) handler
family.  This is affordable since each aggregated recursor handler
doesn't need to be rechecked---look at "STLC_bool.neg_handler", there
are only  new handlers for "tm_true" and the handlers (mundane fields)
from the parent "B.subst_internal.tm_var" have already been type-checked
and inherited (since they only rely on ``the abstracted interface''
module "STLC_409"). 
Thanks to family inheritance, their corresponding compiled module from the parents---for example, 
the module "tm_var_411"---doesn't require another type-check and is
re-used during the type-checking and compilation of "STLC_bool.subst".
For example, for the new "subst", when compiling family "STLC_bool" into
a module, at the appropriate place our plugin will insert
\begin{minted}{Coq}
Definition subst := tm_rec (λ _ ⇒ id → tm → tm) subst_internal.tm_var ...
\end{minted}
where "tm_rec" and "tm" are the corresponding recursor and the (vanilla
but extended and modified) inductive type in that compiled module.\YZ{Where is this "tm" inductive type in figure 6?} Note
that, even though "tm_rec" and "tm" has the same name as before, they
are in the newly-compiled module so they refer to totally different
things.
